\href{https://github.com/Dinesh-Adhithya-H/Computer-Organization/blob/main/Review-Paper-Ryzen-Zen/Ryzen_Zen_Review_Paper.pdf}{\bf 1. Review paper on Ryzen Zen Architecture}
\item The Ryzen Zen Architecture was discussed in terms of its memory hierarchy, core engine, instruction processing pipeline, clock domains and Instruction set. The registers used by the processor, stack operations were discussed in detail and basic operations were written using the instruction set of the architecture. Finally the applications of the processor were discussed.
\\
\\
\href{https://drive.google.com/file/d/1kGVBKwxRkC86UBDCQIcwyQ3t-7vw-IBH/view?usp=sharing}{\bf 2. SMS Spam Detection using Supervised Learning Techniques}
\item Supervised machine learning techniques were used  to classify SMS as spam or not , best performing model had an accuracy of 0.99 and recall of 0.94. The best performing model was a Support Vector Machine with a linear kernel and outperformed logistic regression and Multinomial Naive Bayes.
\\
\\
\href{https://drive.google.com/file/d/1OgF5Zdq66psz5MwVXvDwwPBuZL3PSWPV/view?usp=sharing}{{\bf 3. Pass Difficulty Modelling in Football Matches using Machine Learning Techniques}}
\item Using match event data difficulty of completing passes using various pass characteristics were modelled to identify the best passers of the ball and was used to develop a Xg chain model giving more weight age to tough passes.
\\

\href{https://github.com/Dinesh-Adhithya-H/Natural-Language-Processing/blob/main/Financial-Sentiment-Analysis/Report (2).pdf}{{\bf 4. Financial Text Analysis using WordNet and Supervised Learning Techniques.}}
\item The financial text collected is classified into 3 classes Neutral , Positive and Negative. Various Sentiment Analysis models such as WordNet , Sentiment Intensity Analyzer and bag of words model were explored and best performing model was Support Vector Classifier and performed at 83 \% accuracy.\\

\href{https://github.com/Dinesh-Adhithya-H/Natural-Language-Processing/blob/main/Unsupervised-Opinion-Mining/Report.pdf}{{\bf 4. Opinion Mining using Unsupervised Learning.}}
\item Political opinions of citizens were collected in a survey on the expected qualities of a prime minister. A variety of clustering methods , WordNet based methods , Word embedding based methods were used , the best performing model was a WordNet based model when compared to results compiled by an expert group.


\href{https://github.com/Dinesh-Adhithya-H/Analyzing-Football-Passing-Networks/blob/main/Report/Network%20Science%20Assignment%203.pdf}{{\bf 4. Analyzing football passing networks using network science.}}
\item Passing networks were constructed using two approaches namely using players as nodes and in other space as nodes. Various network centrality measures were measured and a machine learning approach was used to find the importance of these measures and result obtained by a team in a football match. Features such as transitivity and closeness centrality were found to be the most important features leading to a team's win based on a Random Forest Classifier.


\href{https://github.com/Dinesh-Adhithya-H/Reinforcement-Learning/blob/main/avoiding-negative-side-effects-considering-others/Avoiding%20Negative%20Side%20Effects%20by%20Considering%20Others%20(1).pdf}{\bf{ Paper Review on avoiding negative side effects by considering others.}}
\item A two agent environment was built , where one agent's Q function had a caring coefficient on the Q function of the other agent. One of the agent cares about the other agent , but the relationship isn't mutual. Using Q Learning , under various setting of the environment (by tuning caring coefficient) the average rewards obtained for both agents were analyzed.\\

\href{https://github.com/Dinesh-Adhithya-H/Data_Science_and_Machine_Learning/blob/main/MusicGenreClassification/DSML_Final_Project_Report%20Dinesh_Rohit.pdf}{{\bf 4. Music Genre Classification using audio features of the signal.}}
\item Supervised Learning techniques were used to find the important features that distinguish one genre of music from another. Among the models used , Random Forest Classifier performed the best achieving test data set accuracy of 79\%. Features such as variance of spectral centroid and mean of chromagram were found to be important features.
